% !TEX root = knauss-vissuelizer.tex
\section{Conclusion and Future Work}
\todo[inline]{Dana, please review conclusion}
 \viss\ is a visualization tool to analyze requirements clarification in online communication in a project.
Especially agile and distributed projects demand such analysis: agile projects often only sketch requirements in sufficient detail to plan the next iteration and leave the details to be clarified during the development.
Without the ability to measure how this clarification diminishes over time and especially before feature delivery, managers find it hard to manage project risks during iterations.
Our preliminary evaluation has shown that our visualizations allow managers to identify hotspots, e.g. user stories that are not clear to the team. 
Furthermore, \viss\ supports managers in investigating the cause of those hotspots and in identifying suitable actions to disarm problematic or risky situations where the team has insufficient understanding of requirements.
 
In future work, we will evaluate how practitioners use our tool in their daily work. 
This will help us to gain further insight on how managers can use information about requirements clarification over time and to quantify the benefits that tools like the \viss\ can offer.

Such further evaluation should also relate features of online communication (i.e. network centrality, late clarification, no clarification) with typical problems of requirements related discussions, such as feature creep \cite{Jones1996} or symmetry of ignorance \cite{Fischer2000}.

This paper has a complementary video at \url{http://www.youtube.com/watch?v=Oy3xvzjy3BQ&feature=youtu.be}. In addition, the source code of the tool is available at \url{https://github.com/oerich/ReqtDisc}.
\section*{Acknowledgements}
\todo[inline]{There is a number of people we should acknowledge.}