% !TEX root = knauss-vissuelizer.tex
\pdfinfo{/Author (Eric Knauss, Daniela Damian) 
/Title (V:issue:lizer: Explore Online Communication) 
/Subject () 
/Keywords (Requirements clarification patterns; distributed requirements engineering; communication of requirements)}

\title{V:issue:lizer\\Explore Online Communication and  Requirements Clarification over Time}


\author{\IEEEauthorblockN{Eric Knauss, Daniela Damian}
\IEEEauthorblockA{SEGAL, University of Victoria, Victoria B.C., Canada\\
knauss@computer.org, danielad@cs.uvic.ca
}}

\maketitle


\begin{abstract}
In current project environments, requirements often evolve throughout the project and are worked on by stakeholders in large and distributed teams. 
Such teams often use online tools such as mailing lists, bug tracking systems or online discussion forums to communicate, clarify or coordinate work on requirements. 
In this kind of environment, the expected evolution from initial idea, through clarification, to a stable requirement, often stagnates. 
When project managers are not aware of underlying problems, development may proceed before requirements are fully understood and stabilized, leading to numerous implementation issues and often resulting in the need for early redesign and modification.

In this paper, we present the prototype of a tool for analyzing online requirements communication and for supporting our method for the detection and classification of clarification events in requirement discussions. 
We believe that our prototype will be inspire both researchers and practitioners. 
Our v:issue:lizer tool enables researchers to analyze data from our previous studies, relate this data to their research, and use our tool to investigate requirements clarification in other research projects. 
%We used our approach to analyze online requirements communication in the IBM\textsuperscript{\textregistered} Rational Team Concert\textsuperscript{\textregistered} (RTC) project and identified a set of six clarification patterns. 
%\todo[inline]{adjust claim to paper content}
Since a predominant amount of clarifications through the lifetime of a requirement is often indicative of problematic requirements, our v:issue:lizer tool supports project managers to assess, in real-time, the state of discussions around a requirement and promptly react to requirements problems.
\end{abstract}

\begin{IEEEkeywords}
requirements clarification patterns; distributed requirements engineering; communication of requirements
\end{IEEEkeywords}
